\chapter{Chain Mode:}
Chain mode was inspired by old school music trackers that generate music by iterating through sequences and sounds stored in a vertical column.
\section{Why:}
Often you require a sequence that extend for multiple bars and exceed the 64 step limit of the MD. Alternatively, you may wish that both the sequence and sound for a particular track change after some pre-determined interval. Using the MD sequencer you may have achieved these behaviours by chaining multiple patterns together. Chain Mode on the MC improves this ability by allowing you to chain individual tracks together without the need to switch patterns.
\section{How:}
Each slot in the Grid has the ability to play for N loops and then jump to another slot in a specific row of the same column.  These values are specified by the LOOPS and ROW settings in the SlotMenu and apply to the current slot. Jumping between slots is referred to as a transition. Just before a transition occurs, Machine settings are sent to the MD and the internal sequencer data for that track is loaded. All 20 tracks can be configured to transition at the same time.\\
 \\
Chain mode will not send pattern data to the MD. Therefor you must perform all your sequencing using MCL's internal sequencer. For your convenience it is possible to merge a slot's MD sequence data in to the internal sequencer using the SlotMenu->Merge option. Furthermore you can configure the MD to automatically merge sequencer data whenever a slot is saved, by setting GlobalSettings-->MD-->Seq Merge to AUTO.
\section{Enabling Chain Mode}
\textit{ Chain Mode can be enabled in the SlotMenu or GlobalSettings-->ChainMode menu by setting ChainMode to one of 3 three settings: Automatic, Manual and Random.}

\begin{itemize}
	\item Automatic: If the number of loops is greater than 0, slots will automatically jump to the specified Row after N loops.
	\item Manual: Automatic slot jumping is disabled, but tracks can be chained using the quantization rules in the Chain Page.
	\item Random: Slots will jump after a random number of iterations to a random row position bounded by the min and max settings specified in GlobalSettings-->Chain Mode
\end{itemize}


