\chapter{Internal Sequencer:}
MCL features a powerful internal sequencer. There are 16 step sequencer tracks dedicated to the MD and 6 polyphonic tracks dedicated to External Midi devices, each has independent track length and speed.
\section{MD Sequencer Tracks:}
\begin{itemize}
\item 16 Track Sequencer with 64 max steps per track.
\item Conditional Trigs, Slide, Mute and Micro Timing per step.
\item 8 lockable parameters per track with 256 locks available per track. Lockable parameters are MIDI learnt and programmable from the MD.
\item Trigless Locks.
\item Real time record for both step and lock data.
Chromatic Mode. (Machine pitch values are chromatically mapped to the MD. Melodies are recordable)
\end{itemize}
\section{External MIDI Sequencer tracks:}
\begin{itemize}
\item There are 6 x Ext MIDI Sequencer Tracks.
\item Each External MIDI track can be used to sequence an attached MIDI device on port 2. This could be an Elektron Analog 4, Elektron Monomachine or a generic MIDI device such as a synth module.
\item
    Features of the new Ext MIDI Sequencer:
\begin{itemize}
    \item 6 x Tracks
    \item 128 steps per track
	\item 512 events per track.
    \item A maximum of 16 events per step, (i.e 16 note polyphony)
	\item Each event could be an automation parameter or note on/off message.
    \item Microtiming per event
    \item Conditional trig per event
    \item Velocity per step
    \item Each track includes 8 MIDI Control Channel automation parameters with optional slide (linear interpolation).
    \item ProgramChange as CC destination.
\end{itemize}

\section{Auxiliary tracks:}
 AUX Tracks are positioned on Grid B and occupy slots 12 to 15.
  AUX Tracks can be saved/loaded/chained like regular tracks, so that you can automate loading of LFOs, TrackRouting, Machinedrum Master FX and tempo.
 \begin{itemize}
 \item \textbf{MDFXTrack (FX):} Store and recall MDFX (MachinDrum MasterFX: Delay, Reverb, EQ, Dynamics)
 \item \textbf{LFOTrack (LF):} Store and recall LFO page data.
 \item \textbf{RouteTrack (RT):} Store and recall MD Track Routing and Chromatic Mode's Poly settings.
 \item \textbf{TempoTrack (TP):} Store and recall Tempo.

 
    \end{itemize}
\end{itemize}
The internal sequencer is synced to the MIDIClock source.
\\
\chapter{Loading and Saving}
Internal sequencer tracks are automatically mapped to specific slot positions in Grid A or Grid B.\\Slot positions are automatically mapped to specific tracks of the attached MIDI device. \\\\For example:
\begin{enumerate}
    \item The 16 x MD Sequencer tracks are stored/loaded from slots 0 to 15 in Grid A, they correspond to MD tracks 1-16. The MD sequencer tracks can be edited via the StepEdit page.
    \item The 6 x External MIDI Sequencer tracks are stored/loaded from slots 0 to 5 in Grid B. If the Analog4 was attached these would correspond to A4 tracks 1-4. Once loaded, the Ext MIDI tracks can be edited via the Piano Roll editor.
\end{enumerate}
\\
When storing a slot from the Save page, the corresponding internal sequencer track's data is stored, if the slot is mapped to a device such as the MD, the sound data of the corresponding track is retrieved from the device and also saved.\\
\\
Pattern/step sequencer data from an Elektron device is not retained. However, for the Machinedrum, the Save page offers the possibility of copying the corresponding MD track's pattern data to the slot's internal sequencer data via the option MD, or to Merge the MD track's pattern data with the slot's sequencer data. (see next chapter, Save Page)
\\\\
When loading slots using the Load page, the internal sequencer data will be loaded from the slot in to the corresponding sequencer track, the slot's sound data transmitted to the corresponding track on the attached device. If the sequencer is stopped this occurs immediately, If the sequencer is running, then loading occurs according to the chosen quantization option. If the loaded slot contains chain ROW/LOOP chain settings, and Global Chain mode setting is set to AUTO, the next slot transition will occur automatically according to the slot's specified chain settings. (see chapter Chain Mode)


