\chapter{Terminology and Conventions}
   \begin{itemize}
      \item MD - Machinedrum
      \item MDX - Machinedrum X OS.
      \item MC - MegaCommand MIDI controller
      \item MCL - MegaCommand Firmware.
      \item \textbf{<Button> } Enclosed arrows will be used to reference the use of a MegaCommand function button to perform an action.
      \item \textbf{[Key] } Enclosed square bracket will be used to reference the use of a Machinedrum key to perform an action.

      
   \end{itemize}
   
\newpage
\chapter{Key Concepts}

\begin{itemize}
\item \textbf{Page:}
\\
The MCL firmware consists of pages accessible through either the MC's or MD's GUI. Each page contains distinct functionality and is described in this manual.
\item \textbf{Project:}
\\
A project stored on the Micro SD-Card.
The maximum number of projects is only limited by the SD Card capacity.

\item \textbf{Grid:}
\\
The MCL Firmware uses a Grid \& Slot system to store Tracks.\\
Each project contains two grids, X and Y. Grid dimensions are 16 Slots x 128 Rows.\\
\\
Grid X is used to store 16 MD tracks.\\Grid Y is used to store 6 External MIDI tracks + 4 AUX tracks.
\item \textbf{Bank:}\\
The rows of the Grid X are divided in to groups of 16, forming 8 banks A,B,C,D,E,F,G,H.
\item \textbf{Row/Pattern:}
\\
A row of the Grid.

\item \textbf{Slot:}
\\
A position in the Grid where a Track can be stored. (Either occupied or unoccupied).
\item \textbf{Track:}
\\
An MCL sequencer track that may contain both sound and MIDI sequencer data.

There are 3 types of tracks.
\begin{itemize}

\item \textbf{MachineDrum Track} (Grid X: Slots 0-15):
A sequencer track for the Elektron MD. Each MD Track contains the Machine's Sound Settings and Sequencer Data.

\item \textbf{External MIDI Track} (Grid Y: Slots 0-5):
A polyphonic sequencer track used to control a sound module connected via MIDI. Each External MIDI track contains Sequencer Data, and for supported Elektron devices sound data is retained. 

\item \textbf{AUX Track} (Grid Y: Slots: 12-15)\\
An auxiliary track. Used to store/recall the Machinedrum's master FX settings, LFO settings, audio Routing and Tempo settings.
\end{itemize}

\item \textbf{Device:}
An attached MIDI device. The MC supports a unique device on ports 1 and 2.

\item \textbf{Group:}
\\
A collection of slots ordered by the same device type.

\end{itemize}